Estimation of the road traffic sound levels in urban areas based on non-negative matrix factorization techniques

### 2018-02-14 paper/gloaguenNmfTraffic.tex
minor corrections
add endfloat package
Completed abbreviation + break into 2 lines too long url

%%%%%% FIGURE %%%%%%
\usepackage{graphicx}	% insérer des graphiques
\usepackage{subfig}	% utiliser subfigure
\usepackage{float}	% utiliser H dans les figures

@@

%%%%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}	% gérer les adresses www.

@@

\begin{figure}[htp]
  \centering
  \subfloat[]{\label{fig:specW}\includegraphics[height=4cm]{figures/dictionary3.pdf}}
  \hspace{5pt}
  \subfloat[]{\label{fig:ElementW}\includegraphics[height=4cm]{figures/dictionary4.pdf}}
  \caption{Dictionary building on a 3 second extract of a car passage. In dashed lines, a 1 second $w_t$ window  (\ref{fig:specW}). With $w_t$ = 1 second, 3 spectra are then generated and included in $\mathbf{W}$, while for $w_t$ = $all$, the audio file is reduced into 1 spectral vector (\ref{fig:ElementW}).}
  \label{fig:spec_elementW}
\end{figure}

@@

\begin{figure}[t]
  \centering
	\includegraphics[width=\linewidth]{figures/NMF_Lp_alert.pdf}
 \caption{1 second equivalent sound pressure level of an \textit{alert} sub-class scene for 500 Hz low-pass filter and TI-NMF ($\beta$ = 1, $K$ = 200, $w_t$ = 0.5 s, $t$ = 0.42) at $TIR = -12$ dB (in full line) and $TIR$ = 12 dB (in dashed line).}
	\label{fig:lp_alert}
\end{figure}

\begin{figure*}[t]
  \centering
  \subfloat[$MAE$ error for each $TIR$ and sub-class with the frequency low-pass filter with $f_c$ = 500 Hz.]{\label{fig:TIR_class_filter}\includegraphics[width=0.45\textwidth]{figures/filter_bar.pdf}}
  \hspace{5pt}
  \subfloat[$MAE$ error for each $TIR$ and sub-class with Sup-NMF and $\beta$ = 2.]{\label{fig:TIR_class_sup}\includegraphics[width=0.45\linewidth]{figures/sup_bar.pdf}}
  \hspace{5pt}
  \subfloat[$MAE$ error for each $TIR$ and sub-class with Sem-NMF and $\beta$ = 2.]{\label{fig:TIR_class_semi}\includegraphics[width=.45\linewidth]{figures/semi-sup_bar.pdf}}
  \hspace{5pt}
  \subfloat[$MAE$ error for each $TIR$ and sub-class with TI-NMF, $\beta$ = 1 and $t$ = 0.42.]{\label{fig:TIR_class_TI}\includegraphics[width=.45\linewidth]{figures/TI_bar}}
  \caption{$MAE$ (dB) error for each sub-class and each $TIR$ according to the the best results with the filter (\ref{fig:TIR_class_filter}) and each method (Sup-NMF (\ref{fig:TIR_class_sup}), Sem-NMF (\ref{fig:TIR_class_semi}) and TI-NMF (\ref{fig:TIR_class_TI})).}
	\label{fig:TIR_bar}
\end{figure*}
\section{Results}\label{part:results}

@@

\nomenclature{NMF}{Non-negative Matrix Factorization}
\nomenclature{Sup-NMF}{Supervised Non-negative Matrix Factorization}
\nomenclature{Sem-NMF}{Semi-Supervised Non-negative Matrix Factorization}
\nomenclature{TI-NMF}{Thresholded Initialized Non-negative Matrix Factorization}
\nomenclature{$TIR$}{Traffic Interfering Ratio}
\nomenclature{$\mathbf{V}$}{Magnitude spectrogram of the audio sample}
\nomenclature{$\mathbf{\tilde{V}}$}{Approximated spectrogram by the estimator}
\nomenclature{$\mathbf{\tilde{V}}_{traffic}$}{Approximated spectrogram of the traffic by the estimator}
\nomenclature{$\mathbf{W}$}{Dictionary matrix}
\nomenclature{$\mathbf{H}$}{Activation matrix}
\nomenclature{$\mathbf{W_s}$}{Fixed dictionary matrix for Sem-NMF}
\nomenclature{$\mathbf{W_r}$}{Mobile dictionary matrix for Sem-NMF}
\nomenclature{$\mathbf{H_s}$}{Activation matrix for $\mathbf{W_s}$}
\nomenclature{$\mathbf{H_r}$}{Activation matrix for $\mathbf{W_r}$}
\nomenclature{$\mathbf{W_0}$}{Initial dictionary matrix for TI-NMF}
\nomenclature{$\mathbf{W'}$}{Updated dictionary for TI-NMF}
\nomenclature{$MAE$}{Mean Absolute Error (dB)}
\nomenclature{$\mathbf{f_c}$}{Cut-off frequency (Hz)}
\nomenclature{$\mathbf{K}$}{Number of elements in $\mathbf{W}$}
\nomenclature{$\mathbf{w_t}$}{Rectangular window (second)}
\nomenclature{$\mathbf{t}$}{threshold value}
\nomenclature{$\beta$}{Divergence class}
\printnomenclature

\section*{Availability of data and materials}
The dataset supporting the conclusions of this article is available in the \textit{urban$\_$traffic$\_$nmf$\_$dataset.zip}  repository, \url{https://zenodo.org/record/1145855#.Wl2oPnkiGos}. 
The software supporting the conclusions of this article is available in

\begin{itemize}
\item Project name: article2017EstimationAmbiance
\item Project home page: \url{https://github.com/jean-remyGloaguen/article2017EstimationAmbiance}
\item Archived version: \url{https://doi.org/10.5281/zenodo.1145855}
\item Programming language: Matlab
\item Other requirements: Matlab 2016b or higher
\item License: GNU GPL
\item Any restrictions to use by non-academics: license needed 
\end{itemize}

>>>>

%%%%%% FIGURE %%%%%%
\usepackage{graphicx}	% insérer des graphiques
\usepackage{subfig}	% utiliser subfigure
\usepackage{float}	% utiliser H dans les figures
\usepackage[nolists]{endfloat}

@@

%%%%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}	% gérer les adresses www.
\usepackage[hyphenbreaks]{breakurl}

@@

\begin{figure}[t]
  \centering
  \subfloat[]{\label{fig:specW}\includegraphics[height=4cm]{figures/dictionary3.pdf}}
  \hspace{5pt}
  \subfloat[]{\label{fig:ElementW}\includegraphics[height=4cm]{figures/dictionary4.pdf}}
  \caption{Dictionary building on a 3 second extract of a car passage. In dashed lines, a 1 second $w_t$ window  (\ref{fig:specW}). With $w_t$ = 1 second, 3 spectra are then generated and included in $\mathbf{W}$, while for $w_t$ = $all$, the audio file is reduced into 1 spectral vector (\ref{fig:ElementW}).}
  \label{fig:spec_elementW}
\end{figure}

@@

\begin{figure}[t]
  \centering
	\includegraphics[width=\textwidth]{figures/NMF_Lp_alert.pdf}
 \caption{1 second equivalent sound pressure level of an \textit{alert} sub-class scene for 500 Hz low-pass filter and TI-NMF ($\beta$ = 1, $K$ = 200, $w_t$ = 0.5 s, $t$ = 0.42) at $TIR = -12$ dB (in full line) and $TIR$ = 12 dB (in dashed line).}
	\label{fig:lp_alert}
\end{figure}

\begin{figure*}[t]
  \centering
  \subfloat[$MAE$ error for each $TIR$ and sub-class with the frequency low-pass filter with $f_c$ = 500 Hz.]{\label{fig:TIR_class_filter}\includegraphics[width=0.45\textwidth]{figures/filter_bar.pdf}}
  \hspace{5pt}
  \subfloat[$MAE$ error for each $TIR$ and sub-class with Sup-NMF and $\beta$ = 2.]{\label{fig:TIR_class_sup}\includegraphics[width=0.45\linewidth]{figures/sup_bar.pdf}}
  \hspace{5pt}
  \subfloat[$MAE$ error for each $TIR$ and sub-class with Sem-NMF and $\beta$ = 2.]{\label{fig:TIR_class_semi}\includegraphics[width=.45\linewidth]{figures/semi-sup_bar.pdf}}
  \hspace{5pt}
  \subfloat[$MAE$ error for each $TIR$ and sub-class with TI-NMF, $\beta$ = 1 and $t$ = 0.42.]{\label{fig:TIR_class_TI}\includegraphics[width=.45\linewidth]{figures/TI_bar}}
  \caption{$MAE$ (dB) error for each sub-class and each $TIR$ according to the the best results with the filter (\ref{fig:TIR_class_filter}) and each method (Sup-NMF (\ref{fig:TIR_class_sup}), Sem-NMF (\ref{fig:TIR_class_semi}) and TI-NMF (\ref{fig:TIR_class_TI})).}
	\label{fig:TIR_bar}
\end{figure*}

\section{Results}\label{part:results}

@@

\nomenclature{NMF}{Non-negative Matrix Factorization}
\nomenclature{Sup-NMF}{Supervised Non-negative Matrix Factorization}
\nomenclature{Sem-NMF}{Semi-Supervised Non-negative Matrix Factorization}
\nomenclature{TI-NMF}{Thresholded Initialized Non-negative Matrix Factorization}
\nomenclature{$TIR$}{Traffic Interfering Ratio}
\nomenclature{$\mathbf{V}$}{Magnitude spectrogram of the audio sample}
\nomenclature{$\mathbf{\tilde{V}}$}{Approximated spectrogram by the estimator}
\nomenclature{$\mathbf{\tilde{V}}_{traffic}$}{Approximated spectrogram of the traffic by the estimator}
\nomenclature{$\mathbf{V}_{f_c}$}{Approximated spectrogram resulting from the low-pass filter}
\nomenclature{$\mathbf{W}$}{Dictionary matrix}
\nomenclature{$\mathbf{H}$}{Activation matrix}
\nomenclature{$\mathbf{W_f}$}{$k$ element of the dictionary matrix}
\nomenclature{$\mathbf{W_s}$}{Fixed dictionary matrix for Sem-NMF}
\nomenclature{$\mathbf{W_r}$}{Mobile dictionary matrix for Sem-NMF}
\nomenclature{$\mathbf{H_s}$}{Activation matrix related $\mathbf{W_s}$ in Sem-NMF}
\nomenclature{$\mathbf{H_r}$}{Activation matrix for $\mathbf{W_r}$ in Sem-NMF}
\nomenclature{$\mathbf{W_0}$}{Initial dictionary matrix for TI-NMF}
\nomenclature{$\mathbf{W'}$}{Updated dictionary for TI-NMF}
\nomenclature{$MAE$}{Mean Absolute Error (dB)}
\nomenclature{$\mathbf{f_c}$}{Cut-off frequency (Hz)}
\nomenclature{$\mathbf{K}$}{Number of elements in $\mathbf{W}$}
\nomenclature{$\mathbf{w_t}$}{Rectangular window (second)}
\nomenclature{$\mathbf{t}$}{Threshold value}
\nomenclature{$\beta$}{Divergence class}
\printnomenclature

\section*{Availability of data and materials}
The dataset supporting the conclusions of this article is available in the \textit{urban$\_$traffic$\_$nmf$\_$dataset.zip}  repository,  \sloppy \burl{https://zenodo.org/record/1145855#.Wl2oPnkiGos}. 
The software supporting the conclusions of this article is available in

\begin{itemize}
\item Project name: article2017EstimationAmbiance
\item \sloppy Project home page: \burl{https://github.com/jean-remyGloaguen/article2017EstimationAmbiance}
\item Archived version: \url{https://doi.org/10.5281/zenodo.1145855}
\item Programming language: Matlab
\item Other requirements: Matlab 2016b or higher
\item License: GNU GPL
\item Any restrictions to use by non-academics: license needed 
\end{itemize}
